A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-21 doc/paper.tex
Methodology work. Fixes #63, fixes #64.

	\subsection{Design Goals} In visualizing the spreadsheet data, I outlined a few
	core goals for what the tool should accomplish: \begin{itemize} \item [1]
		\textbf{Draw an interactive interface to explore observed function
			combinations.} The combination space for all Excel functions is massive, let
		alone the space for observed formulas. Working from data with actual referents
		in practice, the tool must aid the user in navigating this space. \item [2]
		\textbf{Emphasize the quantitative patterns in formula construction.} The tool,
		accommodating datasets of a few spreadsheets to millions, should address the
		questions of how often the end users employed a certain function and where they
		used it. In this way, it must show precise metrics, such as frequency of  use
		and depth of function nesting, of the dataset it conveys. \item [3]
		\textbf{Promote a qualitative understanding of the patterns.} Lest these
		patterns remain abstract, the tool should supplement its observations with
		concrete instances of relevant formulas from the corpus. Ideally, it should
		even direct users to the exact cell in the spreadsheets where the formula was
		used, contextualizing the functions. \end{itemize} \par

	Likewise, to bound our scope, we outlined a few goals to specifically avoid
	accomplishing with this: \begin{itemize} \item [!1] \textbf{Do not try to
			directly explain what a function does.} Though the tool tries to foster tries
		understanding by linking pattern to example, it won't provide a precise
		description of what a function accomplishes. The tool's user must infer this.
		\item [!2] \textbf{Do not create new formulas.} This is essentially an
		exploratory tool, not a generative one. It should not produce any information
		other than new views of the original data. \item [!3] \textbf{Do not visualize
			individual formulas.} Though there is room to explore the place of a single
		function in the group, the tool must design the core visualization around the
		entire body of data, not the other way around. \end{itemize}

@@

	%To be sure, though, there is still plenty of work to improve this tool. One activity
	%it does not support well now is that of comparison: for all of it's ability to spit
	%out numbers and quantify patterns,

>>>>

	\subsection{Design Goals} In visualizing the spreadsheet data, we outlined the
	core goals for what the tool should accomplish. Furthermore, with these goals,
	we also considered the likely challenges of achieving those goals and 
	particular outcomes which we considered beyond the scope of the research. We present
	both sides of these goals below:

	\begin{itemize}

		\item [1] \textbf{Provide an interactive environment for unguided exploration.}

		%The combination space for all Excel functions is massive, let
		%alone the space for observed formulas. Working from data with actual referents
		%in practice, the tool must aid the user in navigating this space.

		\item [!1] \textbf{Do not make judgments about good and bad design.}

		%Though
		%the tool tries to foster tries understanding by linking pattern to example, it
		%won't provide a precise description of what a function accomplishes. The tool's
		%user must infer this.

		\item [2] \textbf{Emphasize the quantitative patterns in formula construction.}

		%The tool, accommodating datasets of a few spreadsheets to millions, should
		%address the questions of how often the end users employed a certain function
		%and where they used it. In this way, it must show precise metrics, such as
		%frequency of  use and depth of function nesting, of the dataset it conveys.

		\item [!2] \textbf{Do not overwhelm with numbers.}

		%This is essentially an
		%exploratory tool, not a generative one. It should not produce any information
		%other than new views of the original data.

		\item [3] \textbf{Promote a qualitative understanding of the patterns.}

		%Lest
		%these patterns remain abstract, the tool should supplement its observations
		%with concrete instances of relevant formulas from the corpus. Ideally, it
		%should even direct users to the exact cell in the spreadsheets where the
		%formula was used, contextualizing the functions.

		\item [!3] \textbf{Do not attempt to explain formulae.}

		%Though there is room
		%to explore the place of a single function in the group, the tool must design
		%the core visualization around the entire body of data, not the other way
		%around.

	\end{itemize}

@@

	%To be sure, though, there is still plenty of work to improve this tool. One
	% activity
	%it does not support well now is that of comparison: for all of it's ability to
	% spit
	%out numbers and quantify patterns,
